### 2019-10-10 tim-lucas-model-ensembles.tex
Add commented out para table.

\begin{table}[h!]
\caption{Covarage of 80\% credible intervals. Values outside 0.7--0.9 are shown in bold.}
\centering
\begin{tabular}{llrrrrr}
CV & Country &  Enviro & ML\textsubscript{l} &  Enviro + ML\textsubscript{l} & ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Colombia & Random & \textbf{0.28} & \textbf{0.28} & \textbf{0.29} & \textbf{0.29} & \textbf{0.29} \\
 Madagascar &  Random & 0.80 & 0.77& 0.75& 0.77& 0.76 \\
 Senegal & Random &0.79 & 0.79& 0.79& 0.79& 0.82 \\
 Indonesia & Random &0.80 & 0.81& 0.78& 0.79& 0.77  \\
 Colombia &  Spatial & \textbf{0.31} & \textbf{0.34}  & \textbf{0.32} & \textbf{0.34} & \textbf{0.34}  \\
 Madagascar & Spatial & \textbf{0.65} & 0.74& 0.70& 0.75 & 0.76   \\
 Senegal & Spatial & 0.85 & \textbf{0.91}& 0.85& \textbf{0.94} & 0.85  \\
  Indonesia & Spatial & 0.80 & 0.78& 0.78& 0.76& 0.75  \\
\end{tabular}
\label{t:results2}
\end{table}

>>>>

\begin{table}[h!]
\caption{Covarage of 80\% credible intervals. Values outside 0.7--0.9 are shown in bold.}
\centering
\begin{tabular}{llrrrrr}
Country &  CV & Enviro & ML\textsubscript{l} &  Enviro + ML\textsubscript{l} & ML\textsubscript{g} & ML\textsubscript{l} + ML\textsubscript{g} \\
\hline 
 Colombia & Random & \textbf{0.28} & \textbf{0.28} & \textbf{0.29} & \textbf{0.29} & \textbf{0.29} \\
 Madagascar &  Random & 0.80 & 0.77& 0.75& 0.77& 0.76 \\
 Senegal & Random &0.79 & 0.79& 0.79& 0.79& 0.82 \\
 Indonesia & Random &0.80 & 0.81& 0.78& 0.79& 0.77  \\
 Colombia &  Spatial & \textbf{0.31} & \textbf{0.34}  & \textbf{0.32} & \textbf{0.34} & \textbf{0.34}  \\
 Madagascar & Spatial & \textbf{0.65} & 0.74& 0.70& 0.75 & 0.76   \\
 Senegal & Spatial & 0.85 & \textbf{0.91}& 0.85& \textbf{0.94} & 0.85  \\
  Indonesia & Spatial & 0.80 & 0.78& 0.78& 0.76& 0.75  \\
\end{tabular}
\label{t:results2}
\end{table}

%\begin{table}
%\caption{Fitted regression parameters of the environmental and machine learning covariates for thee models: just environmental variables, just local machine learning models and the combination of the two.}
%\centering
%\tiny
%\begin{tabular}{ll|rrr}
%Country    & Variable &  $\beta_{enviro}$   & $\beta_l$ & $\beta_{enviro+l}$\\ \hline
%Madagascar & LST mean & 0.100 & 0.538 &  0.169\\
%Madagascar & EVI & 0.105 & 0.570 & 0.178 \\
%Madagascar & TSI & 0.116 & 0.301 &0.233  \\
%Madagascar & access & 0.113 & 0.033 &0.220  \\
%Madagascar & Elev & 0.109 & 0.469 & 0.205\\ 
%Madagascar & LST sd & 0.116 & 0.301 &0.233  \\
%Madagascar & VIIRS & 0.113 & 0.033 &0.220  \\
%Madagascar & TCW & 0.109 & 0.469 & 0.205\\ 
%Madagascar & RF & 0.100 & 0.538 &  0.169\\
%Madagascar & GBM & 0.105 & 0.570 & 0.178 \\
%Madagascar & enet & 0.116 & 0.301 &0.233  \\
%Madagascar & nnet & 0.113 & 0.033 &0.220  \\
%Madagascar & ppr & 0.109 & 0.469 & 0.205\vspace{0.2cm}\\ 
%Colombia & LST mean & 0.100 & 0.538 &  0.169\\
%Colombia & EVI & 0.105 & 0.570 & 0.178 \\
%Colombia & TSI & 0.116 & 0.301 &0.233  \\
%Colombia & access & 0.113 & 0.033 &0.220  \\
%Colombia & Elev & 0.109 & 0.469 & 0.205\\ 
%Colombia & LST sd & 0.116 & 0.301 &0.233  \\
%Colombia & VIIRS & 0.113 & 0.033 &0.220  \\
%Colombia & TCW & 0.109 & 0.469 & 0.205\\ 
%Colombia & RF & 0.068 & 0.505 &  0.169 \\
%Colombia & GBM & 0.073 & 0.879 & 0.178 \\
%Colombia & enet & 0.070 & 0.079 &0.233 \\
%Colombia & nnet & 0.070 & -0.008 &0.220  \\
%Colombia & ppr & 0.070 & 0.530 & 0.205 \vspace{0.2cm}\\
%Senegal & LST mean & 0.100 & 0.538 &  0.169\\
%Senegal & EVI & 0.105 & 0.570 & 0.178 \\
%Senegal & TSI & 0.116 & 0.301 &0.233  \\
%Senegal & access & 0.113 & 0.033 &0.220  \\
%Senegal & Elev & 0.109 & 0.469 & 0.205\\ 
%Senegal & LST sd & 0.116 & 0.301 &0.233  \\
%Senegal & VIIRS & 0.113 & 0.033 &0.220  \\
%Senegal & TCW & 0.109 & 0.469 & 0.205\\ 
%Senegal & RF & 0.092 & 0.339 & 0.169  \\
%Senegal & GBM & 0.099 & 0.261& 0.178 \\
%Senegal & enet& 0.103 & 0.344  &0.233  \\
%Senegal & nnet & 0.099 & 0.254 &0.220 \\
%Senegal & ppr & 0.098 & 0.268& 0.205 \vspace{0.2cm}\\
%Indonesia & LST mean & 0.100 & 0.538 &  0.169\\
%Indonesia & EVI & 0.105 & 0.570 & 0.178 \\
%Indonesia & TSI & 0.116 & 0.301 &0.233  \\
%Indonesia & access & 0.113 & 0.033 &0.220  \\
%Indonesia & Elev & 0.109 & 0.469 & 0.205\\ 
%Indonesia & LST sd & 0.116 & 0.301 &0.233  \\
%Indonesia & VIIRS & 0.113 & 0.033 &0.220  \\
%Indonesia & TCW & 0.109 & 0.469 & 0.205\\ 
%Indonesia & RF& 0.081 & 0.447 & 0.169 \\
%Indonesia & GBM & 0.085 & 0.357 & 0.178\\
%Indonesia & enet & 0.091 & 0.303 &0.233  \\
%Indonesia & nnet & 0.089 & 0.506 &0.220  \\
%Indonesia & ppr & 0.089 & 0.364 & 0.205 \\
%
%
%
%\end{tabular}
%\label{t:mlresults}
%\end{table}
%
%
